\documentclass[language=en,11pt, openany]{aghdpl}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=blue
}
\usepackage{nomencl}
\usepackage[symbols,sort=none]{glossaries-extra}
\makenomenclature%
\usepackage{tikz} 
\usepackage[demo]{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}%
%-----------------------------------FIRST PAGE-----------------------------------%
\author{Sonia Orlikowska}
\titleEN{A comparative analysis of the use of maze solving algorithms on the example of a dedicated web application}
\thesistype{Master of Science Thesis}
\supervisor{Magdalena Kopernik, PhD, DSc, Assoc. Prof.}
\degreeprogramme{Industrial Computer Science}
\date{2022}
\department{Department of  Applied Computer Science and Modelling}
\faculty{Faculty of Metals Engineering and Industrial Computer Science}
\acknowledgements{Dedicated to the memory of my late brother, Filip, whose absence created the most
 difficult maze of my life. Let this work be the proof that I found a way out of it.}

%-----------------------------------GLOSSARY-----------------------------------%

\glsxtrnewsymbol[description={graph}]{$G$}{\ensuremath{G}}
\glsxtrnewsymbol[description={set of vertices}]{$V$}{\ensuremath{V}}
\glsxtrnewsymbol[description={vertex}]{$v$}{\ensuremath{v}}
\glsxtrnewsymbol[description={vertex neighbour}]{$n$}{\ensuremath{n}}
\glsxtrnewsymbol[description={set of edges}]{$E$}{\ensuremath{E}}
\glsxtrnewsymbol[description={edge}]{$e$}{\ensuremath{e}}
\glsxtrnewsymbol[description={adjacency matrix}]{$A(i,j)$}{\ensuremath{A(i,j)}}
\glsxtrnewsymbol[description={binary tree}]{$B$}{\ensuremath{B}}
\glsxtrnewsymbol[description={spanning tree}]{$T$}{\ensuremath{T}}
\glsxtrnewsymbol[description={vertex degree}]{$d(v)$}{\ensuremath{d(v)}}
\glsxtrnewsymbol[description={degree distribution}]{$P(k)$}{\ensuremath{P(k)}}
\glsxtrnewsymbol[description={k-degree vertex}]{$n_k$}{\ensuremath{n_k}}
\glsxtrnewsymbol[description={clustering coefficient}]{$C_i$}{\ensuremath{C_i}}
\glsxtrnewsymbol[description={Shannon entropy}]{$H(M)$}{\ensuremath{H(M)}}
\glsxtrnewsymbol[description={maze density}]{$r$}{\ensuremath{r}}
\glsxtrnewsymbol[description={path length}]{$p_l$}{\ensuremath{p_l}}
\glsxtrnewsymbol[description={maze}]{$M$}{\ensuremath{M}}
\glsxtrnewsymbol[description={hallway}]{$h$}{\ensuremath{h}}
\glsxtrnewsymbol[description={subset of all v in h}]{$W_h$}{\ensuremath{W_h}}
\glsxtrnewsymbol[description={maze solution}]{$S$}{\ensuremath{S}}
\glsxtrnewsymbol[description={maze starting vertex}]{$p$}{\ensuremath{p}}
\glsxtrnewsymbol[description={Astar Algorithm}]{$A^*$}{\ensuremath{A^*}}
\glsxtrnewsymbol[description={Breadth First Algorithm }]{$BFS$}{\ensuremath{BFS}}
\glsxtrnewsymbol[description={HyperText Markup Language}]{$HTML$}{\ensuremath{HTML}}
\glsxtrnewsymbol[description={Cascading Style Sheets}]{$CSS$}{\ensuremath{CSS}}
\glsxtrnewsymbol[description={Document Object Model}]{$DOM$}{\ensuremath{DOM}}
\glsxtrnewsymbol[description={Continuous Integration/Continuous Delivery}]{$CI/CD$}{\ensuremath{CI/CD}}
\glsxtrnewsymbol[description={Standard Deviation}]{$SD$}{\ensuremath{SD}}

%-----------------------------------NEW THEOREM SET UP-----------------------------------%

\newtheorem{theorem}{Theorem}
%\theorembodyfont{\rm}
\newtheorem{definition}{Definition}
%-----------------------------------BEGINING OF THE DOCUMENT-----------------------------------%
\begin{document}
	\titlepages%
%-----------------------------------ABSTRACT-----------------------------------%	
	\begin{abstract}
\indent In this Master's Thesis, three maze generators and three maze solvers have been investigated and described. Chapter 2 describes in detail the
theoretical foundations derived from Graph Theory, necessary for a precise description of the essence of the studied problems. It shows the most
important parameters describing graphs and mazes, and includes all definitions. All used algorithms are described in detail, along
with the listings.\\
\indent Maze problems and related algorithms are very popular in real-life applications. Chapter 3 presents in detail where discussed algorithms are used,
and how people benefit from them.\\ 
\indent One of the main purposes of this work was also to provide an accurate framework for defining the maze's complexity. The most common idea behind
measuring maze complexity derives only from one concept work. Chapter 4 proves that there are more ways to define maze complexity and that measures of
complexity derived directly from Graph Theory can be used with great success.\\
\indent Chapter 5 presents the collected results and their analysis. This chapter summarizes all obtained work objectives that are consistent with the
assumed objectives. The analysis of the results shows that it is possible to create a framework that allows distinguishing between different mazes
based on their parameters. It is also feasible to evaluate maze complexity by more than the McClendon's measure. Also, Shannon's entropy may be used as a
reliable complexity measure for the studied maze generators. Finally, the conclusions of the results allow providing an answer that the Dijkstra solver
is the best solver for evaluated algorithms, not only for perfect mazes but also for more complicated ones.\\
\indent Chapter 6 presents a detailed description of a web application developed for this work. A lightweight application created in JavaScript allows
visualising the results of the maze generators and solvers described in this work. In the application, it is possible to verify how the described parameters
affect the appearance of the maze, their solutions and the required solution time on dedicated charts, tables and figures.\\
\indent The results and conclusions presented in this work can be used by others to expand research in this area. The framework presented here can be applied
to other types of maze generators and solvers to validate conclusions for other maze problems.\\
\newline
	\textbf{Key words:} Maze, Aldous-Broder, Binary Tree, Recursive- Backtracker, BFS, Dijkstra, Astar, McClendon Complexity, Shannon's entropy
	complexity measure\\
		\end{abstract}
		
       \RedefinePlainStyle%
       \setcounter{tocdepth}{2}
	\tableofcontents
	\printunsrtglossary[type=symbols,style=long,title={List of Symbols}]
	\include{chapter1}
	\include{chapter2}
	\include{chapter3}
    \include{chapter4}
	\include{chapter5}
	\include{chapter6}
	\include{chapter7}
	\include{bibliography}
	\end{document}